Testing Gravity using Type Ia Supernovae Discovered by LSST

### 2018-12-12 doc/article.tex
typo in column header

\begin{abstract}
ZTF today and LSST in the upcoming decade will increase the number of identified  $z<0.3$ Type~Ia supernovae (SNe~Ia)  from the hundreds to the
hundreds of thousands.  The increase in the number density of SNe~Ia, in parallel with improvements in the standardization of
their absolute magnitudes, now make them competitive probes of the growth of structure.
\end{abstract}

@@

\begin{table}
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{|ccc|ccccc|} % Column formatting, @{} suppresses leading/trailing space
   \hline
$z_{max}$ & $\phi$ & $\sigma_{M}$ & $N_{gal}$ & $\bar{A}$ & $\sigma_A$ & $\sigma_A N_{gal}^{-0.5}$ & $\bar{A} \sigma_A^{-1} (18000/760)^{0.5}$ \\
\hline
0.07 & 0.65 & 0.08 & 392 &   1.34 &   0.49 &  0.137 &  13.21 \\
0.07 & 1.00 & 0.08 & 563 &   1.16 &   0.36 &  0.135 &  15.55 \\
0.07 & 1.00 & 0.10 & 563 &   1.27 &   0.48 &  0.112 &  12.88 \\
0.07 & 1.00 & 0.12 & 563 &   1.41 &   0.61 &  0.097 &  11.15 \\
0.07 & 1.00 & 0.15 & 563 &   1.64 &   0.82 &  0.084 &   9.74 \\
0.10 & 0.30 & 0.08 & 429 &   1.26 &   0.51 &  0.120 &  12.09 \\
0.10 & 0.50 & 0.08 & 683 &   1.02 &   0.42 &  0.093 &  11.84 \\
0.10 & 0.65 & 0.08 & 873 &   0.89 &   0.35 &  0.087 &  12.57 \\
0.10 & 0.65 & 0.10 & 873 &   1.01 &   0.46 &  0.075 &  10.72 \\
0.10 & 0.65 & 0.12 & 873 &   1.11 &   0.57 &  0.066 &   9.48 \\
0.10 & 1.00 & 0.08 & 1294 &   0.91 &   0.28 &  0.091 &  15.96 \\
0.10 & 1.00 & 0.10 & 1294 &   0.95 &   0.36 &  0.072 &  12.66 \\
0.10 & 1.00 & 0.12 & 1294 &   1.04 &   0.43 &  0.067 &  11.71 \\
0.15 & 0.30 & 0.08 & 1215 &   1.42 &   0.55 &  0.074 &  12.48 \\
0.15 & 0.30 & 0.12 & 1215 &   1.97 &   0.92 &  0.061 &  10.36 \\
0.15 & 0.50 & 0.08 & 1982 &   1.12 &   0.37 &  0.069 &  14.93 \\
0.15 & 0.65 & 0.08 & 2541 &   1.15 &   0.33 &  0.070 &  17.05 \\
0.15 & 0.65 & 0.10 & 2541 &   1.15 &   0.39 &  0.059 &  14.43 \\
0.15 & 0.65 & 0.12 & 2541 &   1.30 &   0.51 &  0.051 &  12.42 \\
0.15 & 1.00 & 0.08 & 3870 &   1.00 &   0.24 &  0.066 &  20.00 \\
0.20 & 0.20 & 0.08 & 2021 &   1.66 &   0.59 &  0.062 &  13.61 \\
0.20 & 0.30 & 0.08 & 3023 &   1.34 &   0.43 &  0.057 &  15.16 \\
0.20 & 0.30 & 0.10 & 3023 &   1.40 &   0.54 &  0.047 &  12.68 \\
0.20 & 0.30 & 0.12 & 3023 &   1.48 &   0.72 &  0.037 &   9.95 \\
0.20 & 0.50 & 0.08 & 5015 &   1.13 &   0.30 &  0.054 &  18.54 \\
0.20 & 0.65 & 0.08 & 6491 &   1.28 &   0.30 &  0.053 &  20.79 \\
0.20 & 0.65 & 0.10 & 6491 &   1.24 &   0.34 &  0.046 &  17.95 \\
0.20 & 0.65 & 0.12 & 6491 &   1.33 &   0.45 &  0.037 &  14.33 \\
0.20 & 1.00 & 0.08 & 9901 &   1.18 &   0.23 &  0.050 &  24.38 \\
0.20 & 1.00 & 0.10 & 9901 &   1.06 &   0.25 &  0.042 &  20.33 \\
0.20 & 1.00 & 0.12 & 9901 &   1.09 &   0.28 &  0.040 &  19.13 \\
    \hline
   \end{tabular}
   \caption{ston in $A$ or equivalently $f\sigma_8$ for surveys parameterized by the maximum redshift $z_{max}$,
   the fraction of total supernovae in 10 years ``fraction'', intrinsic magnitude dispersion $\sigma_{SN}$.  The number of galaxies
   $N_{gal}$, the signal $\bar{A}$ and its uncertainty $\sigma_A$ are for the cosmoDC2 (v1.0) 760 sq.~deg. volume only.
   The uncertainty ``per'' supernova is given by  $\sigma_A N_{gal}^{-0.5}$.  The ston, scaled to an LSST solid angle, is given as 
    $\bar{A} \sigma_A^{-1} (18000/760)^{0.5}$.
   \label{tab:subsets}}
\end{table}

>>>>

\begin{abstract}
ZTF today and LSST in the upcoming decade will increase the number of identified  $z<0.2$ Type~Ia supernovae (SNe~Ia)  from the hundreds to the
hundreds of thousands.  The increase in the number density of SNe~Ia, in parallel with improvements in the standardization of
their absolute magnitudes, now make them competitive probes of the growth of structure.  The peculiar velocity power spectrum derived from SNe~Ia
is sensitive to the product of the linear growth and amplitude of structure
$f\sigma_8$.  Cross-correlation with synergistic galaxy surveys further constrains $f \sigma_8$ and the galaxy bias.  Velocities
SNe~Ia in the next decade will measure the growth of structure  a powerful test of General Relativity in the local $z<0.2$ Universe.
\end{abstract}

@@

\begin{table}
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{|ccc|ccccc|} % Column formatting, @{} suppresses leading/trailing space
   \hline
$z_{max}$ & $\phi$ & $\sigma_{M}$ & $N_{gal}$ & $\bar{A}$ & $\sigma_A$ & $\bar{A} \sigma_A^{-1} N_{gal}^{0.5}$ & $\bar{A} \sigma_A^{-1} (18000/760)^{0.5}$ \\
\hline
0.07 & 0.65 & 0.08 & 392 &   1.34 &   0.49 &   0.14 &  13.21 \\
0.07 & 1.00 & 0.08 & 563 &   1.16 &   0.36 &   0.13 &  15.55 \\
0.07 & 1.00 & 0.10 & 563 &   1.27 &   0.48 &   0.11 &  12.88 \\
0.07 & 1.00 & 0.12 & 563 &   1.41 &   0.61 &   0.10 &  11.15 \\
0.07 & 1.00 & 0.15 & 563 &   1.64 &   0.82 &   0.08 &   9.74 \\
0.10 & 0.30 & 0.08 & 429 &   1.26 &   0.51 &   0.12 &  12.09 \\
0.10 & 0.50 & 0.08 & 683 &   1.02 &   0.42 &   0.09 &  11.84 \\
0.10 & 0.65 & 0.08 & 873 &   0.89 &   0.35 &   0.09 &  12.57 \\
0.10 & 0.65 & 0.10 & 873 &   1.01 &   0.46 &   0.07 &  10.72 \\
0.10 & 0.65 & 0.12 & 873 &   1.11 &   0.57 &   0.07 &   9.48 \\
0.10 & 1.00 & 0.08 & 1294 &   0.91 &   0.28 &   0.09 &  15.96 \\
0.10 & 1.00 & 0.10 & 1294 &   0.95 &   0.36 &   0.07 &  12.66 \\
0.10 & 1.00 & 0.12 & 1294 &   1.04 &   0.43 &   0.07 &  11.71 \\
0.15 & 0.30 & 0.08 & 1215 &   1.42 &   0.55 &   0.07 &  12.48 \\
0.15 & 0.30 & 0.12 & 1215 &   1.97 &   0.92 &   0.06 &  10.36 \\
0.15 & 0.50 & 0.08 & 1982 &   1.12 &   0.37 &   0.07 &  14.93 \\
0.15 & 0.65 & 0.08 & 2541 &   1.15 &   0.33 &   0.07 &  17.05 \\
0.15 & 0.65 & 0.10 & 2541 &   1.15 &   0.39 &   0.06 &  14.43 \\
0.15 & 0.65 & 0.12 & 2541 &   1.30 &   0.51 &   0.05 &  12.42 \\
0.15 & 1.00 & 0.08 & 3870 &   1.00 &   0.24 &   0.07 &  20.00 \\
0.20 & 0.20 & 0.08 & 2021 &   1.66 &   0.59 &   0.06 &  13.61 \\
0.20 & 0.30 & 0.08 & 3023 &   1.34 &   0.43 &   0.06 &  15.16 \\
0.20 & 0.30 & 0.10 & 3023 &   1.40 &   0.54 &   0.05 &  12.68 \\
0.20 & 0.30 & 0.12 & 3023 &   1.48 &   0.72 &   0.04 &   9.95 \\
0.20 & 0.50 & 0.08 & 5015 &   1.13 &   0.30 &   0.05 &  18.54 \\
0.20 & 0.65 & 0.08 & 6491 &   1.28 &   0.30 &   0.05 &  20.79 \\
0.20 & 0.65 & 0.10 & 6491 &   1.24 &   0.34 &   0.05 &  17.95 \\
0.20 & 0.65 & 0.12 & 6491 &   1.33 &   0.45 &   0.04 &  14.33 \\
0.20 & 1.00 & 0.08 & 9901 &   1.18 &   0.23 &   0.05 &  24.38 \\
0.20 & 1.00 & 0.10 & 9901 &   1.06 &   0.25 &   0.04 &  20.33 \\
0.20 & 1.00 & 0.12 & 9901 &   1.09 &   0.28 &   0.04 &  19.13 \\
    \hline
   \end{tabular}
   \caption{ston in $A$ or equivalently $f\sigma_8$ for surveys parameterized by the maximum redshift $z_{max}$,
   the fraction of total supernovae in 10 years ``fraction'', intrinsic magnitude dispersion $\sigma_{SN}$.  The number of galaxies
   $N_{gal}$, the signal $\bar{A}$ and its uncertainty $\sigma_A$ are for the cosmoDC2 (v1.0) 760 sq.~deg. volume only.
   The uncertainty ``per'' supernova is given by  $\sigma_A N_{gal}^{-0.5}$.  The ston, scaled to an LSST solid angle, is given as 
    $\bar{A} \sigma_A^{-1} (18000/760)^{0.5}$.
   \label{tab:subsets}}
\end{table}
